Bootstrap learning via modular concept discovery

### 2013-04-22 drafts/ijcai2013/ijcai13.tex
Changed bibliography style to named, using the named.bst file.
Changed intro motivating example from baking to circuit building.

\section{Introduction}
A central question for AI is how to create intelligent agents without
building in vast amounts of pre-specified knowledge that is tailored
to one domain or another. Any attempt to solve this problem must
contend with the fact that the less an agent knows about solving
problems in a domain, the worse its attempts are, and, therefore, the
less informative they are about how to solve subsequent problems. For
example, imagine you know nothing about baking but are supplied with a
stocked kitchen: your initial attempts will be uniformly inedible, and
you will learn little from them. If, on the other hand, you know the
basics, you are far more likely to generate recipes that are
somewhat successful and on whose basis you might improve your skills.

Like many of the problems in AI, this one can be cast as a search
problem: the goal is to find a baking procedure that maximizes certain
criter.  There are many search algorithms, but they typically exploit
local or topological structure in the search space. For example, local
search algorithms move from one candidate solution to a neighboring
one. Heuristic search techniques take advantage of topological
structure to prune off large parts of the solution space.

@@

%% The file named.bst is a bibliography style file for BibTeX 0.99c
\bibliographystyle{plain}
\bibliography{ijcai13}
%% \nocite{*}

>>>>

\section{Introduction}
A central question for AI is how to create intelligent agents without
building in vast amounts of pre-specified knowledge that is tailored
to one domain or another. Any attempt to solve this problem must
contend with the fact that the less an agent knows about solving
problems in a domain, the worse its attempts are, and, therefore, the
less informative they are about how to solve subsequent problems.

For example, imagine you know nothing about electronics but are
supplied with a collection of circuit elements and asked to build a
useful device: your initial attempts will be uniformly
ineffective. If, on the other hand, you know the basics, you are far
more likely to generate devices that are somewhat successful and on
whose basis you might improve your skills.

Like many of the problems in AI, this one can be cast as a search
problem: the goal is to find a circuit wiring procedure that maximizes
certain criteria.  There are many search algorithms, but they typically
exploit local or topological structure in the search space. For
example, local search algorithms move from one candidate solution to a
neighboring one. Heuristic search techniques take advantage of
topological structure to prune off large parts of the solution space.

@@

%% The file named.bst is a bibliography style file for BibTeX 0.99c
\bibliographystyle{named}
\bibliography{ijcai13}
%% \nocite{*}
